\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-19 icse/intro.tex
Reflected Jihyeok's comments

Researchers have defined various JavaScript formal
semantics~\cite{aplas08,lambdajs,kjs,javert} and developed several static
analyzers on top of them~\cite{jsai,tajs,wala,safe}.  As illustrated
in Figure~\ref{fig:existing}, they defined their own Intermediate
Representations (IRs) to represent JavaScript program semantics.  They
built parsers to construct Abstract Syntax Trees (ASTs) from
programs and AST-IR translators to convert ASTs
to their own IRs.  This approach helps researchers focus on IRs
without worrying about diverse and enormous features of JavaScript in
developing new techniques for program analysis and formal verification.
We dub such a methodology that manipulates language semantics by first
translating given programs to IRs that are suitable for analysis and
verification \textit{IR-based semantics extraction}.

@@

In this paper, we propose JavaScript IR-based Semantics Extraction
Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
syntax and semantics from the ECMAScript specification.  It
automatically generates a JavaScript parser from the syntax defined in
the ECMAScript specification.  It also automatically extracts the
formal semantics of JavaScript with given \textit{compile rules}.
Each compile rule describes how abstract algorithms in the
specification written in a natural language are converted into
functions of our intermediate representation \( \ires \).  In
addition, to save the labor of defining such compile rules, we also
present a \textit{rule generation assistant}, which suggests new
compile rules based on statistical analysis of not yet convertible
algorithms.  The assistant helps us deal with changed or newly
introduced algorithms defined in new versions of the ECMAScript
specification as well.

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, test262~\cite{test262}; out of \inred{XXXXX} tests for
ECMAScript 2020 it passed \inred{XXXXX} tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  We applied
\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
passed all the tests in \inred{XX} proposals and partially passed the
tests in \inred{XX} proposals.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found \inred{X} possible specification errors in ECMAScript
2020; we reported them to TC39 and \inred{X} errors were confirmed and
the remaining \inred{X} errors are under review.
\end{itemize}

>>>>

Researchers have defined various JavaScript formal
semantics~\cite{aplas08,lambdajs,kjs,javert} and developed several static
analyzers on top of them~\cite{jsai,tajs,wala,safe}.  As illustrated
in Figure~\ref{fig:existing}, they defined their own Intermediate
Representations (IRs) to represent JavaScript program semantics.  They
built parsers to construct Abstract Syntax Trees (ASTs) from
programs and AST-IR translators to convert ASTs
to their own IRs.  This approach helps researchers focus on IRs
without worrying about diverse and enormous features of JavaScript in
developing new techniques for program analysis and formal verification.
We dub such a methodology that manipulates language semantics by
translating given programs to IRs that are suitable for analysis and
verification \textit{IR-based semantics extraction}.

@@

In this paper, we propose JavaScript IR-based Semantics Extraction
Toolchain (\( \tool \)), which \textit{automatically} extracts JavaScript
syntax and semantics from the ECMAScript specification.  It
automatically generates a JavaScript parser from the syntax defined in
the ECMAScript specification.  It also automatically extracts the
formal semantics of JavaScript with given \textit{compile rules}.
Each compile rule describes how abstract algorithms in the
specification written in a natural language are converted into
functions of our intermediate representation \( \ires \).  In
addition, to save the labor of defining such compile rules, we also
present a \textit{rule generation assistant}, which suggests new
compile rules based on fault localization of not yet convertible
algorithms.  The assistant helps us deal with changed or newly
introduced algorithms defined in new versions of the ECMAScript
specification as well.

The main contribution of this paper is \( \tool \):
\begin{itemize}[leftmargin=0.5cm]
\item We successfully applied \( \tool \) to ECMAScript 2020, the next
ECMAScript version scheduled to be released in June 2020.  The
automatically extracted semantics passed the official conformance test
suite, test262~\cite{test262}; out of \inred{XXXXX} tests for
ECMAScript 2020 it passed \inred{XXXXX} tests.
\item \( \tool \) is also applicable to new language features proposed
for a future release to aid language development in a modular way.
Because ECMAScript is an open standard language, various proposals are
available with their own specification changes and tests.  We applied
\( \tool \) to such proposals; out of \inred{XX} proposals, the tool
passed all the tests in \inred{XX} proposals and partially passed the
tests in \inred{XX} proposals.
\item Moreover, since the extraction mechanism of \( \tool \) is fully
automatic, we can use it to find possible specification errors.  We
indeed found \inred{X} possible specification errors in ECMAScript
2020.  They were all confirmed by TC39 and will be fixed in the next
release.
\end{itemize}
